---
title: "Daily information summary of economic indicators available from FRED, FRB St. Louis"
author: "Paul G. Smith"
date: '`r paste("First created on Oct 31, 2019. Updated on", format(Sys.Date(),"%b %d, %Y"))`'
output: 
  github_document:
    toc: true
    html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Daily information summary of economic indicators available from FRED, FRB St. Louis


```{r echo=TRUE, message=TRUE, warning=TRUE}
source("Dependencies.R", echo = TRUE)
source("Functions.R", echo = TRUE)

```

### `r now() %>% format('%A')` Morning Update: `r now() %>% format('%B %d, %Y')`


### 1. Six-Month Change in Major Stock Indexes

```{r echo=TRUE, message=TRUE, warning=TRUE}
source("001_Six month indexes.R", echo = TRUE)
```

### 2. WTI Crude Oil Price

```{r echo=TRUE, message=TRUE, warning=TRUE}
source("002_WTI crude oil price.R", echo = TRUE)
```

### 3. Regular Gasoline Price

```{r echo=TRUE, message=TRUE, warning=TRUE}
source("003_Gas gulf coast regular price.R", echo = TRUE)
```

### 4. Gasoline % of Oil Price

```{r echo=TRUE, message=TRUE, warning=TRUE}
source("004_Gas percent of oil.R", echo = TRUE)
```

### 5. ULS #2 Diesel Price

```{r echo=TRUE, message=TRUE, warning=TRUE}
source("005_ULS 2 diesel price.R", echo = TRUE)
```

### 6. Price of Gold

```{r echo=TRUE, message=TRUE, warning=TRUE}
source("006_Price of gold.R", echo = TRUE)
```

### 7. Price of Silver

```{r echo=TRUE, message=TRUE, warning=TRUE}
source("007_Price of silver.R", echo = TRUE)
```

### 8. 4-Wk Moving Avg Unemployment Initial Claims

```{r echo=TRUE, message=TRUE, warning=TRUE}
source("008_Unemployment initial claims.R", echo = TRUE)
```

### 9. Breakeven Inflation, 5-Year

```{r echo=TRUE, message=TRUE, warning=TRUE}
source("009_Breakeven inflation.R", echo = TRUE)
```

### Finally, Print the Plots for `r now() %>% format('%A')` Morning Update: `r now() %>% format('%B %d, %Y')`


```{r echo=FALSE, message=FALSE, warning=FALSE}
source("200_Print report.R", echo = FALSE)
```